---
title: "modown definition and usage"
author: "Vincent Bonhomme"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{modown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Rationale
Morphometrics data essentially consist of coordinates and, if any, associated covariates.

Existing morphometrics file format exist, eg `.tps`, `.nts`, `.xml`, etc. but (in y humble opinion) none is fully satisfactory.

I propose here the `.coo` file format along with R utilities.

Just like markdown, `modown` has minimalist syntax and is easy to read/manipulate/write both for humans and machines.

Modown a pun on markdown and Momocs and a tribute to Motown.

## Specifications
`.coo` files are plain text files whose single line syntax fall within rules:

1. space-separated numbers (eg `-0.5 0.5`) stand for coordinates  (and other numeric data) in each dimension;
2. a word and a number or word (eg `size 3.14`) associate a covariate name and its value;
3. a single word (eg `ldk`) introduce a partition of coordinates;
4. a tilde (~) and word (eg `turtle1`:) names a shape name when several are collated in the same file.
5. nothing or something else (eg `# a comment`) is ignored.

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
